An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-03-03 EconGrowthSeminar.Rnw
Starting to include the outline for the seminar. Added a Calvin heart-and-hand logo to the presentation.

\mode<presentation>
{
  \usetheme{Berkeley}
  \usecolortheme{beaver}
  % or ...

  \setbeamercovered{transparent}
  % or whatever (possibly just delete it)

  \setbeamercolor{section number projected}{bg=red,fg=gray}
  \setbeamercolor{itemize item} {bg=red, fg=gray}
}

@@

\author[Caleb Reese, Lucas Timmer, Matthew Heun] % (optional, use only with lots of authors)
%{F.~Author\inst{1} \and S.~Another\inst{2}}
{Caleb Reese, Lucas Timmer, Matthew Kuperus Heun}
% - Use the \inst{?} command only if the authors have different
%   affiliation.

@@

\date[Short Occasion] % (optional)
{4 April 2013 / Mathematics Department Colloquium}

\subject{Talks}
% This is only inserted into the PDF information catalog. Can be left
% out.

% If you have a file called "university-logo-filename.xxx", where xxx
% is a graphic format that can be processed by latex or pdflatex,
% resp., then you can add a logo as follows:

% \pgfdeclareimage[height=0.5cm]{university-logo}{university-logo-filename}
% \logo{\pgfuseimage{university-logo}}

@@

\section{Introduction}

\subsection[Short First Subsection Name]{First Subsection Name}

\begin{frame}{Make Titles Informative. Use Uppercase Letters.}{Subtitles are optional.}
  % - A title should summarize the slide in an understandable fashion
  %   for anyone how does not follow everything on the slide itself.

  \begin{itemize}
  \item
    Use \texttt{itemize} a lot.
  \item
    Use very short sentences or short phrases.
  \end{itemize}
\end{frame}

\begin{frame}{Make Titles Informative.}

  You can create overlays\dots
  \begin{itemize}
  \item using the \texttt{pause} command:
    \begin{itemize}
    \item
      First item.
      \pause
    \item    
      Second item.
    \end{itemize}
  \item
    using overlay specifications:
    \begin{itemize}
    \item<3->
      First item.
    \item<4->
      Second item.
    \end{itemize}
  \item
    using the general \texttt{uncover} command:
    \begin{itemize}
      \uncover<5->{\item
        First item.}
      \uncover<6->{\item
        Second item.}
    \end{itemize}
  \end{itemize}
\end{frame}

\subsection{Second Subsection}

\begin{frame}{Make Titles Informative.}
\end{frame}

\begin{frame}{Make Titles Informative.}
\end{frame}

\section*{Summary}

\begin{frame}{Summary}

>>>>

\mode<presentation>
{
  \usetheme{Berkeley}
  \usecolortheme{beaver}
  % or ...
  \setbeamercolor{section number projected}{bg=gray,fg=red}
  \setbeamercolor{itemize item} {bg=gray, fg=red}
  \setbeamercolor{itemize subitem} {bg=gray, fg=red}
  \setbeamercolor{itemize subsubitem} {bg=gray, fg=red}

  % \setbeamercovered{transparent}
  % or whatever (possibly just delete it)  
}

@@

\author[Reese, Timmer, Heun] % (optional, use only with lots of authors)
{Caleb Reese, Lucas Timmer, Matthew Kuperus Heun}
%{F.~Author\inst{1} \and S.~Another\inst{2}}
% - Use the \inst{?} command only if the authors have different
%   affiliation.

@@

\date[Math Seminar] % (optional)
{Mathematics Colloquium\\
4 April 2013
}

\subject{Energy and Economic Growth}
% This is only inserted into the PDF information catalog. Can be left
% out.

% If you have a file called "university-logo-filename.xxx", where xxx
% is a graphic format that can be processed by latex or pdflatex,
% resp., then you can add a logo as follows:
% \pgfdeclareimage[height=0.5cm]{university-logo}{university-logo-filename}
% \logo{\pgfuseimage{university-logo}}

\pgfdeclareimage[height=1.53cm]{university-logo}{CalvinLogo.png}
\logo{\pgfuseimage{university-logo}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection[Growth Modeling]{Economic Growth Modeling} %+++++++++++++++++++++++++++++++++++++++

% \begin{frame}{Make Titles Informative. Use Uppercase Letters.} %----------------------------
%   % - A title should summarize the slide in an understandable fashion
%   %   for anyone how does not follow everything on the slide itself.
% 
%   \begin{itemize}
%   \item
%     Use \texttt{itemize} a lot.
%   \item
%     Use very short sentences or short phrases.
%   \end{itemize}
% \end{frame}
% 
% \begin{frame}{Make Titles Informative.} %----------------------------
% 
%   You can create overlays\dots
%   \begin{itemize}
%   \item using the \texttt{pause} command:
%     \begin{itemize}
%     \item
%       First item.
%       \pause
%     \item    
%       Second item.
%     \end{itemize}
%   \item
%     using overlay specifications:
%     \begin{itemize}
%     \item<3->
%       First item.
%     \item<4->
%       Second item.
%     \end{itemize}
%   \item
%     using the general \texttt{uncover} command:
%     \begin{itemize}
%       \uncover<5->{\item
%         First item.}
%       \uncover<6->{\item
%         Second item.}
%     \end{itemize}
%   \end{itemize}
% \end{frame}

\subsection{Types of Energy} %+++++++++++++++++++++++++++++++++++++++

\begin{frame}{Thermal Energy ($Q$)} %----------------------------

\end{frame}

\begin{frame}{Exergy ($X$)} %----------------------------

\end{frame}

\begin{frame}{Useful Work ($W$)} %----------------------------

\end{frame}

\subsection{Economic Growth Models} %+++++++++++++++++++++++++++++++++++++++

\begin{frame}{Single Factor} %----------------------------

\end{frame}

\begin{frame}{Cobb-Douglas} %----------------------------

\end{frame}

\begin{frame}{Constant Elasticity of Substitution (CES)} %----------------------------

\end{frame}

\begin{frame}{LINEX} %----------------------------

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Sources of Data}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection[Econ Data]{Sources of Economic Data} %+++++++++++++++++++++++++++++++++++++++

\subsection[Energy Data]{Sources of Energy Data} %+++++++++++++++++++++++++++++++++++++++

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Examples}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection[US]{USA} %+++++++++++++++++++++++++++++++++++++++

\subsection[ZA]{South Africa} %+++++++++++++++++++++++++++++++++++++++

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Summary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Summary} %----------------------------
